---
title: "prerequisites_for_following_examples"
output: md_document
---
```{r}
library(rtweet)
library(tidyverse)
library(lubridate)
```

# Prerequisites for following the example track

To follow the coding examples, make sure you have installed and loaded the following packages:

## tidyverse
The package "tidyverse" is an umbrella package loading several libraries that are all handy in terms of working with data. For further information on and learning to use tidyverse see https://www.tidyverse.org. 

Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” Journal of Open Source Software, 4(43), 1686. doi: 10.21105/joss.01686


## lubridate
The package lubridate is used for handling different date formats in R and doing operations on them. The package in from the same group behind the package "tidyverse", but is not a core package in the "tidyverse". 

Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with lubridate. Journal of Statistical Software, 40(3), 1-25. URL https://www.jstatsoft.org/v40/i03/.

## jsonlite
The package "jsonlite" is for handling the dataformat Javascript Object Notation (json), which is a format used for exchanging data on the internet. For more information on the jsonlite-package see https://cran.r-project.org/web/packages/jsonlite/index.html

If you already have a JSON file containing your twitter data, you can use the `fromJSON`-function in the `jsonlite`-package to upload the data into your R environment.

Ooms J (2014). “The jsonlite Package: A Practical and Consistent Mapping Between JSON Data and R Objects.” arXiv:1403.2805 [stat.CO]. https://arxiv.org/abs/1403.2805.

## Recomendations for acqurring your twitter data

### rtweet
The package "rtweet" is an implementation of calls designed to collect and organize Twitter data via Twitter's REST and stream Application Program Interfaces (API), which can be found at the following URL:
    <https://developer.twitter.com/en/docs>.

"Kearney, M. W. (2019). rtweet: Collecting and analyzing Twitter data,", "Journal of Open Source Software, 4, 42. 1829.", "(R package version 0.7.0)", "https://joss.theoj.org/papers/10.21105/joss.01829".

If you have not already acquired some twitter data and wish to follow the coding examples step-by-step, you can use your twitter account and the `search_tweets()`-function from the "rtweet"-package to import twitter data into your R environment. This will return up to 18000 tweets from the past 10 days. Copy the code chunk bellow, to generate a dataframe based on a free-text search on the term "sesamestreet".

```{r}
sesamestreet_data <- search_tweets(q = "sesamestreet", n = 18000)
```
