---
title: "2_tidslig udvikling"
output: html_document
---

# Timedispersion analysis with twitterdata

```{r}
library(rtweet)
library(tidyverse)
library(lubridate)
```
# Acuirreing your data
In the following example, you will learn how to process and visualize data acquired from Twitter.com using the Essential access Twitter API. 
In this example, you will create your dataframe by making a free-text search on the term "sesamestreet" using the `search_tweets()`-function from the "rtweet"-package. 

```{r}
sesamestreet_data <- search_tweets(q = "sesamestreet", n = 18000)
```

# Timely dispersion of hashtags and fretext
In the following we start of with some data processing before moving on to the actual visualisation. The question we are asking the data here is a two-piece one. 

* First of we want to know the dispersion of the tweets over time. 
* Second we want to know how many of these contain a the hashtag "#sesamestreet". 

Especially the last question needs some data wranglig before it is possible to answer it. The process here is to create a new column which has the value "TRUE" if the tweet contains the hashtag and FALSE if not. This is done with the `mutate()`-function, which creates a new column called "has_sesame_ht". To put the TRUE/FALSE-values in this column we use the  `str_detect()`-function. This function is told that it is detecting on the column "text", which contains the tweet. Next it is told what it is detecting. Here we use the `regex()`-function within `str_detect()` and by doing that we can specify that we are interested in all variants of the hashtag (eg #SesameStreet, #Sesamestreet, #sesamestreet, #SESAMESTREET, etc.).  This is achieved by setting "ignore_case = TRUE".

The next step is another `mutate()`-function, where we create a new column "date". This column will contain just the date of the tweets instead of the entire timestamp from Twitter that not only contains the date, but also the hour, minute and second of the Tweet. This is obtained with the `date()`-function from the "lubridate"-packages, which is told that it should extract the date from the "created_at"-column.  
Lastly we use the `count`-function from the "tidyverse"-package to count TRUE/FALSE-values in the "has_same_ht"-column per day in the data set. 

```{r}
sesamestreet_data %>% 
  mutate(has_sesame_ht = str_detect(text, regex("#sesamestreet", ignore_case = TRUE))) %>% 
  mutate(date = date(created_at)) %>% 
  count(date, has_sesame_ht)
```
This is the result we now want to visualise. In the code below we have appended the code for the visualisation to the four lines of code above that transforms the data to our needs.  
To pick up where we left in the previous code chunk we continue with the `ggplot()`-function, which is the graphics package of the "tidyverse". This function is told that it should put date on the x-axis and the counted number of TRUE/FALSE-values on the y-axis. The next line of the creation of the visualisation is `geom_line()`,where we specify linetype=has_sesame_ht, thus creating creating two lines for; one for TRUE and one for FALSE. 

The lines of code following the `geom_line()` argument tweaks the aesthetics of the visualisation. `scale_linetype()`tells R, what the lines should be labeled as. `scale_x_date()` and `scale_y_continuous()` changes the looks of the x- and y-axis respectively. At last, the `labs()` and `guides()` arguments are used to create descriptive text on the visualisation. 

Remember to inspect your data in your R environment and adjust these labels to fit your acquired data. 

```{r}
sesamestreet_data%>% 
  mutate(has_sesame_ht = str_detect(text, regex("#sesamestreet", ignore_case = TRUE))) %>% 
  mutate(date = date(created_at)) %>% 
  count(date, has_sesame_ht) %>% 
  ggplot(aes(date, n)) +
  geom_line(aes(linetype=has_sesame_ht)) +
  scale_linetype(labels = c("No #sesamestreet", "#sesamestreet")) +
  scale_x_date(date_breaks = "1 day", date_labels = "%b %d") +
  scale_y_continuous(breaks = seq(0, 30000, by = 5000)) +
  theme(axis.text.x=element_text(angle=40, hjust=1)) +
  labs(title = "Figure 1 - Daily tweets dispersed on whether or not they\ncontain #sesamestreet", y="Number of Tweets", x="Day", subtitle = "Period: 4 december 2021 - 13 december 2021", caption = "Total number of tweets: 2.413") +
  guides(linetype = guide_legend(title = "Whether or not the\ntweet contains \n#sesamestreet"))
```
You should now have a graph dipicting the timely dispersion of tweets in your dataset.

In the next codechunk you can save the plot as a png-file for further use:

```{r}
ggsave("20211213_sesamestreet_2021_tweet_timeline_dispersed_on_hastag_or_not.png", width = 8, height = 5, dpi = 800)
```

